Dynein walks like an Imperial AT-ST

### 2018-03-22 papers/paper/paper.tex

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_foot_order_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_foot_order_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}

>>>>

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}

\begin{figure*}[tbhp]
    \includegraphics[width=0.5\linewidth]{../../plots/paper_static_foot_order_histogram}
    \includegraphics[width=0.5\linewidth]{../../plots/paper_exponential_foot_order_histogram}
\caption{The left plot is the $C=0$ case where the unbinding rate is
  independent of angle.  Here ``alternating'' means that the binding
  domain which did not move last time moved this time.  Passing means
  that the moving foot was behind, and ended up in front.}
\label{fig:steppingorder}
\end{figure*}
